%%%%%%%%%%%%%%%%%%%%%%%
%%%%%  Conclusion %%%%%
%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Conclusion} \label{Ch:Conclusion}
In this thesis, the usage of \emph{Fourier-Net}, \emph{Fourier-Net+} and \emph{4xFourier-Net+} for efficient and fast registration of subsampled MRI data was explored. This research question was approached from multiple different angles examining registration both directly, comparing the networks to traditional algorithms and other neural networks, as well as indirectly as part of a motion-compensated reconstruction pipeline. \\
After training the networks on subsampled MRI data, multiple experiments were described to examine the research question. These included ablation studies and parameter tests on the \emph{ACDC} dataset followed by downstream tests on the \emph{CMRxRecon} dataset. While the latter was for testing the applicability of the networks, the parameter tests were used to determine optimal network parameters for \emph{Fourier-Net}, \emph{Fourier-Net+} and \emph{4xFourier-Net+}. Then, their registration performance was compared to \emph{NiftyReg}, a traditional registration algorithm, and \emph{VoxelMorph}, a state-of-the-art neural network. For the second part of experiments, the three networks were used as part of an motion-compensated reconstruction pipeline. For this, the \emph{CMRxRecon} dataset was used as it contained the needed k-space data and subsampling masks. We simulated motion for a downstream test using a motion-compensated reconstruction pipeline. Two different approaches were used to simulate mis-triggering and non-linear lung motion between frames. These were then reconstructed using a pipeline with neural networks for motion-compensation. The three networks were again compared to \emph{VoxelMorph} in this downstream test.\\
Our results showed that \emph{Fourier-Net}, \emph{Fourier-Net+} and \emph{4xFourier-Net+} regularly outperform \emph{NiftyReg} and \emph{VoxelMorph} for registration performance on subsampled data, as well as \emph{VoxelMorph} for the motion-compensation reconstruction-pipeline. Advantages of \emph{Fourier-Net+} and \emph{4xFourier-Net+} in terms of memory efficiency were highlighted together with excellent inference speeds in the low milliseconds for all neural networks. Limitations, like the use of image similarity metrics instead of e.g. the more objective Dice score on the \emph{CMRxRecon} dataset as well as the simulation of synthetic motion for the downstream test, were discussed. In the future, we plan to extend the networks to 3D and extend the test with the reconstruction pipeline to data with real lung motion. In conclusion, the research question can be answered positively as the networks performed well on the subsampled data. Still, there are further improvements to be made and some experiments could be repeated with more realistic data to further validate the results obtained in this thesis.